Music Perception 1: Variability Analysis

### 2021-07-02 analysis/variability.Rmd
update variability analysis (look at each recording, which creates a large CV for KOT)
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

# Data analysis
- Pearson's correlation (if normality is violated, Spearman's rank correlation instead) between variability measurements and participants' judgments as "teaching"

@@

>>>>

# Variability
- Pearson's correlation (if normality is violated, Spearman's rank correlation instead) between variability measurements and participants' judgments as "teaching"

@@

# Appendix

## deviated CVs based on legato
```{r kot-extra-1, echo = FALSE}
cv_deviated_legato <- cv_kot_leg[abs(CV) > 10]

# a_p_16
a_p_16 <- dt_kot[MidFile == cv_deviated_legato[1]$MidFile]
a_p_16$Interval <- c(1:nrow(a_p_16))

ggline(a_p_16, x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_16") +
  scale_x_continuous(breaks = seq(1,66,1))

ggline(a_p_16[Subcomponent == "Legato"], x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_16 (Legato)") +
  scale_x_continuous(breaks = seq(1,66,1))

ggline(a_p_16[Subcomponent == "Staccato"], x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_16 (Staccato)") +
  scale_x_continuous(breaks = seq(1,66,1))

# a_p_16
a_p_6 <- dt_kot[MidFile == cv_deviated_legato[2]$MidFile]
a_p_6$Interval <- c(1:nrow(a_p_6))

ggline(a_p_6, x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_6") +
  scale_x_continuous(breaks = seq(1,66,1))

ggline(a_p_6[Subcomponent == "Legato"], x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_6 (Legato)") +
  scale_x_continuous(breaks = seq(1,66,1))

ggline(a_p_6[Subcomponent == "Legato"], x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_ (Staccato)") +
  scale_x_continuous(breaks = seq(1,66,1))

# a_p_15
a_p_15 <- dt_kot[MidFile == cv_deviated_legato[3]$MidFile]
a_p_15$Interval <- c(1:nrow(a_p_15))

ggline(a_p_15, x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_15") +
  scale_x_continuous(breaks = seq(1,66,1))

ggline(a_p_15[Subcomponent == "Legato"], x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_15 (Legato)") +
  scale_x_continuous(breaks = seq(1,66,1))

ggline(a_p_15[Subcomponent == "Staccato"], x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_15 (Staccato)") +
  scale_x_continuous(breaks = seq(1,66,1))

# a_p_24
a_p_24 <- dt_kot[MidFile == cv_deviated_legato[4]$MidFile]
a_p_24$Interval <- c(1:nrow(a_p_24))

ggline(a_p_24, x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_24") +
  scale_x_continuous(breaks = seq(1,66,1))

ggline(a_p_24[Subcomponent == "Legato"], x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_24 (Legato)") +
  scale_x_continuous(breaks = seq(1,66,1))

ggline(a_p_24[Subcomponent == "Staccato"], x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_24 (Staccato)") +
  scale_x_continuous(breaks = seq(1,66,1))
```

## stable CVs based on legato
```{r kot-extra-2, echo = FALSE}
cv_stable_legato <- cv_kot_leg[abs(CV) < 0.5]

# a_p_2
a_p_2 <- dt_kot[MidFile == cv_stable_legato[1]$MidFile]
a_p_2$Interval <- c(1:nrow(a_p_2))

ggline(a_p_2, x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_2") +
  scale_x_continuous(breaks = seq(1,66,1))

ggline(a_p_2[Subcomponent == "Legato"], x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_2 (Legato)") +
  scale_x_continuous(breaks = seq(1,66,1))

ggline(a_p_2[Subcomponent == "Staccato"], x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_2 (Staccato)") +
  scale_x_continuous(breaks = seq(1,66,1))

# a_p_4
a_p_4 <- dt_kot[MidFile == cv_stable_legato[2]$MidFile]
a_p_4$Interval <- c(1:nrow(a_p_4))

ggline(a_p_4, x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_4") +
  scale_x_continuous(breaks = seq(1,66,1))

ggline(a_p_4[Subcomponent == "Legato"], x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_4 (Legato)") +
  scale_x_continuous(breaks = seq(1,66,1))

ggline(a_p_4[Subcomponent == "Staccato"], x = "Interval", y = "KOT", position = position_dodge(.2), xlab = "Interval", ylab = "KOT (ms)", title = "a_p_4 (Staccato)") +
  scale_x_continuous(breaks = seq(1,66,1))
```
